---
title: "Marginal Effects"
output:
  html_document:
    df_print: paged
  word_document: default
---

In this analysis we run multiple linear models to explore the relation between the dependent variables and group. To explore the effect of age we also run the same model using age as covariate and the we compare the two models using [test_likelihoodratio](https://easystats.github.io/performance/reference/test_likelihoodratio.html).

After finding the best models (all the model are better including age) we look at the interaction between group and age for all the variables. We use the package [modelbased](https://easystats.github.io/modelbased/reference/estimate_slopes.html) to extract the marginal effects. Modelbased's estimate_slope is a wrapper around Emmeans' [emtrends](https://rdrr.io/cran/emmeans/man/emtrends.html)

# Preparation

Read and prepare the data to be analyzed

```{r, message=FALSE}
### Importing libraries
library(easystats)  # to compute estimate slopes and check model assumptions
library(car)        # to extract anova table from linear models
library(haven)      # to read spss database files
library(tidyverse)    # plotting library
library(patchwork)
library(ggrepel)

# Custom palettes
palette1 <- c("#559ad1", "#ffb621",  "#CC79A7","#F46036")
palette2 = c('black','azure4')
```

After importing the libraries we read the data

```{r, message=FALSE}
### Read data
input = 'C:\\Users\\tomma\\OneDrive - Birkbeck, University of London\\VirtualTools_Rewards_2022\\SPSS\\database\\'
output = 'C:\\Users\\tomma\\OneDrive - Birkbeck, University of London\\VirtualTools_Rewards_2022\\Analysis\\R_analysis\\Plots\\'

Time = read_sav(paste(input, 'DatabaseSRATTTIME_2.sav', sep=''))
Switch = read_sav(paste(input, 'databasetoolswitching.sav', sep=''))
Distance = read_sav(paste(input, 'databasedistance.sav', sep=''))
Ntools = read_sav(paste(input, 'databasenbtool.sav', sep=''))

## making sure group is a factor and not a integer

Time$group      = factor(Time$group)
Switch$group    = factor(Switch$group)
Distance$group  = factor(Distance$group)
Ntools$group    = factor(Ntools$group)
```

We now can run the analysis. We will start by looking at the Time domain

# Analysis

## Time

### Success Rate

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Model the data using simple linear model
Time.mod1.sr = lm(sr~group, data =  Time )
Time.mod2.sr = lm(sr~age*group, data =  Time )

# Compare the two models with or without age
# this show the model with age is better
test_likelihoodratio(Time.mod1.sr,Time.mod2.sr)

# Extracting parameters linear model
parameters(Time.mod2.sr)

# In case we prefer we can also extract an anova table
Anova(Time.mod2.sr, type='III')

# Checks model assumptions
ck1 = plot(check_normality(Time.mod2.sr),type = "qq")
ck2 = plot(check_outliers(Time.mod2.sr))
ck1/ck2

### estimate slopes
slope_Time.mod.sr = estimate_slopes(Time.mod2.sr, at = 'group')
slope_Time.mod.sr
```

**Plotting the results**\
Here we plot the result of our analysis.\
On top the plot of our model, raw data (dots) and the estimate of the model (line).\
On the bottom the plot of the estimated marginal means.

```{r, fig.height=8.3, fig.width=11.7, fig.align='center', dpi = 300}

# make preparation for the slope data-frame
slopePlot = slope_Time.mod.sr %>%
  mutate(P = case_when(
    p >= 0.05 ~ '', 
    p < 0.05 & p >= 0.01 ~ '*',
    p < 0.01 & p >= 0.001 ~ '**',
    p < 0.001 ~ '***'),
    R = paste( c("\U03B2:","\U03B2:","\U03B2:"), as.character(round(Coefficient,3))))

# Model plot
T1.1 = Time %>%
  bind_cols( as.data.frame(get_predicted(Time.mod2.sr, ci=0.95))) %>%
  ggplot( aes(x=age, y=Predicted, color = group))+
    geom_point(aes(y=sr), size=7)+
    geom_line(linewidth = 4.5)+
    geom_text(inherit.aes = F, data =slopePlot, aes(x = 10, y=115, label = R), size = 12)+
    geom_text( inherit.aes = F, data =slopePlot, aes(x = 10, y=105, label = P), size = 18)+
    facet_wrap(~ group, labeller = labeller(group = 
      c('1' = 'PRG',
        '2' = 'NRG',
        '3' = 'Control')))+
    labs(x = 'Years', y = 'Success rate (%)')+
    ylim(NA, 120)+
    theme_classic(base_size = 40)+
    theme(axis.line = element_blank(),legend.position = "none")+
    scale_colour_manual(values=palette1)
ggsave(paste(output,'SuccesRate.jpg', sep = ''), T1.1, width = 1920*3, height = 1080*3, units = "px", dpi = 300)

# Marginal Effect plot
T1.2 = slopePlot %>%
  mutate(Significance = ifelse(p < 0.05, "True", "False")) %>%
  ggplot( aes(x = group, y = Coefficient, color = Significance))+
  geom_hline(yintercept = 0, linewidth=1.3, linetype = "dashed")+
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), size=2.4, linewidth=1.5)+
  theme_classic(base_size = 40)+
  theme(axis.line = element_blank(),legend.position = "bottom")+
  scale_x_discrete(name=NULL,label = c('PRG','NRG','Control'))+
  coord_cartesian(xlim = c(1.12, 2.92))+
  scale_colour_manual(values=palette2)+
  labs(y = 'Effect of Age')+
  scale_y_continuous(n.breaks=4)
ggsave(paste(output,'slope_Time_sr_plot.jpg', sep = ''), T1.2, width = 1920*3, height = 1080*3, units = "px", dpi = 300)


combT1 = T1.1 / T1.2 +
  plot_layout(heights = c(2, 1.2))

ggsave(paste(output,'SuccesRateCombo.jpg', sep = ''),combT1 , width = 1920*3, height = 1080*3, units = "px", dpi = 300)


combT1
```

### Time per attempt

No significant result for time per attempt

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Model the data using simple linear model
Time.mod1.timeattempt = lm(timeperattempt~group, data =  Time )
Time.mod2.timeattempt = lm(timeperattempt~age*group, data =  Time )

# Compare the two models with or without age
# both models here are not significative I'll use the 
# one with age but doesn't make a lot of sense
test_likelihoodratio(Time.mod2.timeattempt,Time.mod1.timeattempt)

# Extracting parameters linear model
parameters(Time.mod1.timeattempt)

# In case we prefer we can also extract an anova table
Anova(Time.mod1.timeattempt, type='III')

# Checks model assumptions
ck1 = plot(check_normality(Time.mod1.timeattempt),type = "qq")
ck2 = plot(check_outliers(Time.mod1.timeattempt))
ck1/ck2
```
**Plotting the results**\
Here we plot the result of our analysis.\
On top the plot of our model, raw data (dots) and the estimate of the model (line).\
On the bottom the plot of the estimated marginal means.

```{r, fig.height=8.3, fig.width=11.7, fig.align='center', dpi = 300}
# Model plot

Mean.T2 = as.data.frame(estimate_means(Time.mod1.timeattempt))
Mean.T2$M = paste( c('M:','M:','M:'), as.character(round(Mean.T2$Mean,1)))

T2 = ggplot(Time, aes(x=group, y = timeperattempt, color = group ))+
  geom_point(position = position_jitterdodge(),size=7, alpha=0.35)+
  geom_pointrange(inherit.aes = F, data = Mean.T2 , aes(x= group, y = Mean, ymin = Mean-SE, ymax = Mean+SE, color = group), size=3,linewidth=2.5)+
  geom_text(inherit.aes = F, data = Mean.T2, aes(x =c(1.3,2.3,3.3), y= Mean, label= M),size = 10)+
  scale_colour_manual(values=palette1)+
  scale_x_discrete(label = c('PRG','NRG','Control'))+
  scale_y_continuous(labels=function(x)x/1000)+
  labs(y = "Attempt time (sec)")+
  coord_cartesian(xlim = c(1.13, 2.9))+
  theme_classic(base_size = 40)+
  theme(axis.line = element_blank(),legend.position = "none",
        axis.title.x = element_blank())


ggsave(paste(output,'TimePerAttempt.jpg', sep = ''), T2 , width = 1920*3, height = 1080*3, units = "px", dpi = 300)
T2
```
### Attempt per trial

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Model the data using simple linear model
Time.mod1.attempttr = lm(attemptpertrial~group, data =  Time )
Time.mod2.attempttr = lm(attemptpertrial~age*group, data =  Time )

# Compare the two models with or without age
# this show the model with age is better
test_likelihoodratio(Time.mod1.attempttr,Time.mod2.attempttr)

# Extracting parameters linear model
parameters(Time.mod2.attempttr)

# In case we prefer we can also extract an anova table
Anova(Time.mod2.attempttr, type='III')

# Checks model assumptions
ck1 = plot(check_normality(Time.mod2.attempttr),type = "qq")
ck2 = plot(check_outliers(Time.mod2.attempttr))
ck1/ck2

### estimate slopes
slope_Time.mod.attempttr = estimate_slopes(Time.mod2.attempttr, at = 'group')
slope_Time.mod.attempttr
```

**Plotting the results**\
Here we plot the result of our analysis.\
On top the plot of our model, raw data (dots) and the estimate of the model (line).\
On the bottom the plot of the estimated marginal means.

```{r, fig.height=8.3, fig.width=11.7, fig.align='center', dpi = 300}

# make preparation for the slope data-frame
slopePlot = slope_Time.mod.attempttr %>%
  mutate(P = case_when(
    p >= 0.05 ~ '', 
    p < 0.05 & p >= 0.01 ~ '*',
    p < 0.01 & p >= 0.001 ~ '**',
    p < 0.001 ~ '***'),
    R = paste( c("\U03B2:","\U03B2:","\U03B2:"), as.character(round(Coefficient,3))))

# Model plot
T3.1 = Time %>%
  bind_cols( as.data.frame(get_predicted(Time.mod2.attempttr, ci=0.95))) %>%
  ggplot( aes(x=age, y=Predicted, color = group))+
    geom_point(aes(y=attemptpertrial), size=7)+
    geom_line(linewidth = 4.5)+
    geom_text(inherit.aes = F, data =slopePlot, aes(x = 10, y=6.8, label = R), size = 12)+
    geom_text( inherit.aes = F, data =slopePlot, aes(x = 10, y=6.2, label = P), size = 18)+
    facet_wrap(~ group, labeller = labeller(group = 
      c('1' = 'PRG',
        '2' = 'NRG',
        '3' = 'Control')))+
    labs(x = 'Years', y = '# of attempts')+
    ylim(NA, 7.1)+
    theme_classic(base_size = 40)+
    theme(axis.line = element_blank(),legend.position = "none")+
    scale_colour_manual(values=palette1)
ggsave(paste(output,'AttemptsPerTrial.jpg', sep = ''), T3.1, width = 1920*3, height = 1080*3, units = "px", dpi = 300)

# Marginal Effect plot
T3.2 = slopePlot %>%
  mutate(Significance = ifelse(p < 0.05, "True", "False")) %>%
  ggplot( aes(x = group, y = Coefficient, color = Significance))+
  geom_hline(yintercept = 0, linewidth=1.3, linetype = "dashed")+
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), size=2.4, linewidth=1.5)+
  theme_classic(base_size = 40)+
  theme(axis.line = element_blank(),legend.position = "bottom")+
  scale_x_discrete(name=NULL,label = c('PRG','NRG','Control'))+
  coord_cartesian(xlim = c(1.12, 2.92))+
  scale_colour_manual(values=palette2)+
  labs(y = 'Effect of Age')+
  scale_y_continuous(n.breaks=4)
ggsave(paste(output,'slope_Time_attempttr_plot.jpg', sep = ''), T3.2, width = 1920*3, height = 1080*3, units = "px", dpi = 300)
 
combT3 = T3.1 / T3.2 +
  plot_layout(heights = c(2, 1.2))

ggsave(paste(output,'AttemptsPerTrialCombo.jpg', sep = ''),combT3 , width = 1920*3, height = 1080*3, units = "px", dpi = 300)
combT3
```

## Tool switching

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Model the data using simple linear model
Switch.mod1 = lm(toolswitching~group, data =  Switch )
Switch.mod2 = lm(toolswitching~age*group, data =  Switch )

# Compare the two models with or without age
# this show the model with age is better
test_likelihoodratio(Switch.mod1,Switch.mod2)

# Extracting parameters linear model
parameters(Switch.mod2)

# In case we prefer we can also extract an anova table
Anova(Switch.mod2, type='III')

# Contrast analysis for the group level
estimate_contrasts(Switch.mod2)

# Checks model assumptions
ck1 = plot(check_normality(Switch.mod2),type = "qq")
ck2 = plot(check_outliers(Switch.mod2))
ck1/ck2

### estimate slopes
slope_Switch.mod = estimate_slopes(Switch.mod2, at = 'group')
slope_Switch.mod
```

**Plotting the results**\
Here we plot the result of our analysis.\
On top the plot of our model, raw data (dots) and the estimate of the model (line).\
On the bottom the plot of the estimated marginal means.

```{r, fig.height=8.3, fig.width=11.7, fig.align='center', dpi = 300}

# make preparation for the slope data-frame
slopePlot = slope_Switch.mod %>%
  mutate(P = case_when(
    p >= 0.05 ~ '', 
    p < 0.05 & p >= 0.01 ~ '*',
    p < 0.01 & p >= 0.001 ~ '**',
    p < 0.001 ~ '***'),
    R = paste( c("\U03B2:","\U03B2:","\U03B2:"), as.character(round(Coefficient,3))))


# Model Plot
Ts.1 = Switch %>%
  bind_cols( as.data.frame(get_predicted(Switch.mod2, ci=0.95))) %>%
  ggplot( aes(x=age, y=Predicted, color = group))+
    geom_point(aes(y=toolswitching), size=7)+
    geom_line(linewidth = 4.5)+
    geom_text(inherit.aes = F, data =slopePlot, aes(x = 10, y=118, label = R), size = 12)+
    geom_text( inherit.aes = F, data =slopePlot, aes(x = 10, y=96, label = P), size = 18)+
    facet_wrap(~ group, labeller = labeller(group = 
      c('1' = 'PRG',
        '2' = 'NRG',
        '3' = 'Control')))+
    labs(x = 'Years', y = 'Tool switching (%)')+
    ylim(NA,123)+
    theme_classic(base_size = 40)+
    theme(axis.line = element_blank(),legend.position = "none")+
    scale_colour_manual(values=palette1)
ggsave(paste(output,'ToolSwitching.jpg', sep = ''), Ts.1, width = 1920*3, height = 1080*3, units = "px", dpi = 300)

# Marginal Effect plot
Ts.2 = slopePlot %>%
  mutate(Significance = ifelse(p < 0.05, "True", "False")) %>%
  ggplot( aes(x = group, y = Coefficient, color = Significance))+
  geom_hline(yintercept = 0, linewidth=1.3, linetype = "dashed")+
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), size=2.4, linewidth=1.5)+
  theme_classic(base_size = 40)+
  theme(axis.line = element_blank(),legend.position = "bottom")+
  scale_x_discrete(name=NULL,label = c('PRG','NRG','Control'))+
  coord_cartesian(xlim = c(1.12, 2.92))+
  scale_colour_manual(values=palette2)+
  labs(y = 'Effect of Age')+
  scale_y_continuous(n.breaks=4)
ggsave(paste(output,'slope_Switch_plot.jpg', sep = ''), Ts.2, width = 1920*3, height = 1080*3, units = "px", dpi = 300)
 
combTs = Ts.1 / Ts.2 +
  plot_layout(heights = c(2, 1.2))

ggsave(paste(output,'ToolSwitchingCombo.jpg', sep = ''),combTs , width = 1920*3, height = 1080*3, units = "px", dpi = 300)
combTs
```

## Number of tools

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Model the data using simple linear model
Ntools.mod1 = lm(nbtool~group, data =  Ntools )
Ntools.mod2 = lm(nbtool~age*group, data =  Ntools )

#Compare the two models with or without age
# this show the model with age is better
test_likelihoodratio(Ntools.mod1,Ntools.mod2)

# Extracting parameters linear model
parameters(Ntools.mod2)

# In case we prefer we can also extract an anova table
Anova(Ntools.mod2, type='III')

# Contrast analysis for the group level
estimate_contrasts(Ntools.mod2)

# Checks model assumptions
ck1 = plot(check_normality(Ntools.mod2),type = "qq")
ck2 = plot(check_outliers(Ntools.mod2))
ck1/ck2

### estimate slopes
slope_Ntools.mod= estimate_slopes(Ntools.mod2, at = 'group')
slope_Ntools.mod
```

**Plotting the results**\
Here we plot the result of our analysis.\
On top the plot of our model, raw data (dots) and the estimate of the model (line).\
On the bottom the plot of the estimated marginal means.

```{r, fig.height=8.3, fig.width=11.7, fig.align='center', dpi = 300}

# make preparation for the slope data-frame
slopePlot = slope_Ntools.mod %>%
  mutate(P = case_when(
    p >= 0.05 ~ '', 
    p < 0.05 & p >= 0.01 ~ '*',
    p < 0.01 & p >= 0.001 ~ '**',
    p < 0.001 ~ '***'),
    R = paste( c("\U03B2:","\U03B2:","\U03B2:"), as.character(round(Coefficient,3))))

# Model Plot
N.1 = Ntools %>%
  bind_cols( as.data.frame(get_predicted(Ntools.mod2, ci=0.95))) %>%
  ggplot( aes(x=age, y=Predicted, color = group))+
    geom_point(aes(y=nbtool), size=7)+
    geom_line(linewidth = 4.5)+
    geom_text(inherit.aes = F, data =slopePlot, aes(x = 10, y=3.6, label = R), size = 12)+
    geom_text( inherit.aes = F, data =slopePlot, aes(x = 10, y=3.05, label = P), size = 18)+
    facet_wrap(~ group, labeller = labeller(group = 
      c('1' = 'PRG',
        '2' = 'NRG',
        '3' = 'Control')))+
    labs(x = 'Years', y = '# of tools')+
    ylim(NA, 3.8)+
    theme_classic(base_size = 40)+
    theme(axis.line = element_blank(),legend.position = "none")+
    scale_colour_manual(values=palette1)
ggsave(paste(output,'NumberOfTools.jpg', sep = ''), N.1, width = 1920*3, height = 1080*3, units = "px", dpi = 300)

# Marginal Effect plot
N.2 = slopePlot %>%
  mutate(Significance = ifelse(p < 0.05, "True", "False")) %>%
  ggplot( aes(x = group, y = Coefficient, color = Significance))+
  geom_hline(yintercept = 0, linewidth=1.3, linetype = "dashed")+
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), size=2.4, linewidth=1.5)+
  theme_classic(base_size = 40)+
  theme(axis.line = element_blank(),legend.position = "bottom")+
  scale_x_discrete(name=NULL,label = c('PRG','NRG','Control'))+
  coord_cartesian(xlim = c(1.12, 2.92))+
  scale_colour_manual(values=palette2)+
  labs(y = 'Effect of Age')+
  scale_y_continuous(n.breaks=4)
ggsave(paste(output,'slope_Ntools_plot.jpg', sep = ''), N.2, width = 1920*3, height = 1080*3, units = "px", dpi = 300)

combN = N.1 / N.2 +
  plot_layout(heights = c(2, 1.2))

ggsave(paste(output,'NumberOfToolsCombo.jpg', sep = ''),combN , width = 1920*3, height = 1080*3, units = "px", dpi = 300)
combN
```

## Distance

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Model the data using simple linear model
Distance.mod1 = lm(distance~group, data =  Distance )
Distance.mod2 = lm(distance~age*group, data =  Distance )

#Compare the two models with or without age
# this show the model with age is better
test_likelihoodratio(Distance.mod1,Distance.mod2)

# Extracting parameters linear model
parameters(Distance.mod2)

# In case we prefer we can also extract an anova table
Anova(Distance.mod2, type='III')

# Contrast analysis for the group level
estimate_contrasts(Distance.mod2)

# Checks model assumptions
ck1 = plot(check_normality(Distance.mod2),type = "qq")
ck2 = plot(check_outliers(Distance.mod2))
ck1/ck2

### estimate slopes
slope_Distance.mod= estimate_slopes(Distance.mod2, at = 'group')
slope_Distance.mod
```

**Plotting the results**\
Here we plot the result of our analysis.\
On top the plot of our model, raw data (dots) and the estimate of the model (line).\
On the bottom the plot of the estimated marginal means.

```{r, fig.height=8.3, fig.width=11.7, fig.align='center', dpi = 300}

# make preparation for the slope data-frame
slopePlot = slope_Distance.mod %>%
  mutate(P = case_when(
    p >= 0.05 ~ '', 
    p < 0.05 & p >= 0.01 ~ '*',
    p < 0.01 & p >= 0.001 ~ '**',
    p < 0.001 ~ '***'),
    R = paste( c("\U03B2:","\U03B2:","\U03B2:"), as.character(round(Coefficient,3))))

# Model plot
D.1 = Distance %>%
  bind_cols( as.data.frame(get_predicted(Distance.mod2, ci=0.95))) %>%
  ggplot( aes(x=age, y=Predicted, color = group))+
    geom_point(aes(y=distance), size=7)+
    geom_line(linewidth = 4.5)+
      geom_text(inherit.aes = F, data =slopePlot, aes(x = 10, y=320, label = R), size = 12)+
    geom_text( inherit.aes = F, data =slopePlot, aes(x = 10, y=265, label = P), size = 18)+
    facet_wrap(~ group, labeller = labeller(group = 
      c('1' = 'PRG',
        '2' = 'NRG',
        '3' = 'Control')))+
    ylim(NA, 335)+
    labs(x = 'Years', y = 'Distance (pixels)')+
    theme_classic(base_size = 40)+
    theme(axis.line = element_blank(),legend.position = "none")+
    scale_colour_manual(values=palette1)
ggsave(paste(output,'Distance.jpg', sep = ''), D.1, width = 1920*3, height = 1080*3, units = "px", dpi = 300)

# Marginal Effect plot
D.2 = slopePlot %>%
  mutate(Significance = ifelse(p < 0.05, "True", "False")) %>%
  ggplot( aes(x = group, y = Coefficient, color = Significance))+
  geom_hline(yintercept = 0, linewidth=1.3, linetype = "dashed")+
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), size=2.4, linewidth=1.5)+
  theme_classic(base_size = 40)+
  theme(axis.line = element_blank(),legend.position = "bottom")+
  scale_x_discrete(name=NULL,label = c('PRG','NRG','Control'))+
  coord_cartesian(xlim = c(1.12, 2.92))+
  scale_colour_manual(values=palette2)+
  labs(y = 'Effect of Age')+
  scale_y_continuous(n.breaks=4)
ggsave(paste(output,'slope_Distance_plot.jpg', sep = ''), D.1, width = 1920*3, height = 1080*3, units = "px", dpi = 300)
 
combD = D.1 / D.2 +
  plot_layout(heights = c(2, 1.2))

ggsave(paste(output,'DistanceCombo.jpg', sep = ''),combD , width = 1920*3, height = 1080*3, units = "px", dpi = 300)
combD
```

## FinalPlot

Putting together all the plots

```{r, fig.height=23, fig.width=11.7, fig.align='center', dpi = 300}
# Define the plots
T1.1 = T1.1 + theme(axis.line = element_blank(), strip.background = element_blank(), strip.text.x = element_blank())
T1.2 = T1.2 + theme(axis.line = element_blank(),axis.text.x=element_blank(),legend.position = "none",axis.ticks.x=element_blank())
T3.1 = T3.1 + theme(axis.line = element_blank(), strip.background = element_blank(), strip.text.x = element_blank())
T3.2 = T3.2 + theme(axis.line = element_blank(), legend.position = "bottom")

# Arrange the plots
comb1 = T1.1 / T1.2 /plot_spacer()/ T3.1 / T3.2 +
  plot_layout(heights = c(2, 1, 0.35,2, 1))+
  plot_annotation(tag_levels = list(c('A','','B',''))) &
  theme(plot.tag = element_text(size = 60), plot.tag.position  = c(-0.06, 1),
        plot.margin = margin(1, 1, 1, 2, "cm"))

comb1

ggsave(paste(output,'FinalPlot_Time.jpg', sep = ''),comb1 , width = 1920*3, height = 1080*8, units = "px", dpi = 300)
ggsave(paste(output,'FinalPlot_Time.svg', sep = ''),comb1 , width = 1920*3, height = 1080*8, units = "px", dpi = 300)
ggsave(paste(output,'FinalPlot_Time.tiff', sep = ''),comb1 , width = 1920*3, height = 1080*8, units = "px", dpi = 300)
```

```{r, fig.height=23, fig.width=11.7, fig.align='center', dpi = 300}
Ts.1_p = Ts.1 + theme(axis.line = element_blank(), strip.background = element_blank(), strip.text.x = element_blank())
Ts.2_p = Ts.2 + theme(axis.line = element_blank(),axis.text.x=element_blank(),legend.position = "none",axis.ticks.x=element_blank())
N.1_p = N.1 + theme(axis.line = element_blank(), strip.background = element_blank(), strip.text.x = element_blank())
N.2_p = N.2 + theme(axis.line = element_blank(),axis.text.x=element_blank(),legend.position = "none",axis.ticks.x=element_blank())
D.1_p = D.1 + theme(axis.line = element_blank(), strip.background = element_blank(), strip.text.x = element_blank())
D.2_p = D.2 + theme(axis.line = element_blank(), legend.position = "bottom")

# Arrange the plots
comb2 = Ts.1_p / Ts.2_p / plot_spacer() / N.1_p / N.2_p / plot_spacer()/D.1_p/ D.2_p+
  plot_layout(heights = c(2, 1, .4, 2, 1, .4,2, 1))+
  plot_annotation(tag_levels = list(c('A','','B','', 'C',''))) &
  theme(plot.tag = element_text(size = 60), plot.tag.position  = c(-0.06, 1),
        plot.margin = margin(1, 1, 1, 2, "cm"))

comb2

ggsave(paste(output,'FinalPlot_Int.jpg', sep = ''), comb2, width = 1920*3, height = 1080*8, units = "px", dpi = 300)
ggsave(paste(output,'FinalPlot_Int.svg', sep = ''), comb2, width = 1920*3, height = 1080*8, units = "px", dpi = 300)
ggsave(paste(output,'FinalPlot_Int.tiff', sep = ''), comb2, width = 1920*3, height = 1080*8, units = "px", dpi = 300)

```
