---
title: "Basic Analysis"
output:
  html_document:
    df_print: paged
  word_document: default
---

In this analysis we run multiple anovas variables and group. After running the anova we perform a Tukey HSD test to check for significant differences between groups.

# Preparation

Read and prepare the data to be analyzed

```{r, message=FALSE}
### Importing libraries
library(easystats)  # to compute estimate slopes and check model assumptions
library(haven)      # to read spss database files
library(tidyverse)    # plotting library
library(patchwork)  # to combine plots
library(ggrepel)
library(ggsignif)

# Custom palettes
palette1 <- c("#559ad1", "#ffb621",  "#CC79A7","#F46036")
palette2 = c('black','azure4')
```

After importing the libraries we read the data

```{r, message=FALSE}
### Read data
input = 'C:\\Users\\tomma\\OneDrive - Birkbeck, University of London\\VirtualTools_Rewards_2022\\SPSS\\database\\'
output = 'C:\\Users\\tomma\\OneDrive - Birkbeck, University of London\\VirtualTools_Rewards_2022\\Analysis\\R_analysis\\Plots\\'

Time = read_sav(paste(input, 'DatabaseSRATTTIME_2.sav', sep=''))
Switch = read_sav(paste(input, 'databasetoolswitching.sav', sep=''))
Distance = read_sav(paste(input, 'databasedistance.sav', sep=''))
Ntools = read_sav(paste(input, 'databasenbtool.sav', sep=''))

## making sure group is a factor and not a integer

Time$group      = factor(Time$group)
Switch$group    = factor(Switch$group)
Distance$group  = factor(Distance$group)
Ntools$group    = factor(Ntools$group)
```

# Basic anova analysis

## Time

### Success Rate

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}

##### Anova
Time.aov.sr <- aov(sr ~ group, data = Time)

summary(Time.aov.sr)
report(Time.aov.sr)

# Checks model assumptions
ck1 = plot(check_normality(Time.aov.sr),type = "qq")
ck2 = plot(check_outliers(Time.aov.sr))
ck1/ck2

# Perform the Tukey HSD test
posthoc.sr <- TukeyHSD(Time.aov.sr)

# Print the results
print(posthoc.sr)
```

### Time per attempt

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Anova
Time.aov.timeperattempt <- aov(timeperattempt ~ group, data = Time)

summary(Time.aov.timeperattempt)
report(Time.aov.timeperattempt)

# Checks model assumptions
ck1 = plot(check_normality(Time.aov.timeperattempt),type = "qq")
ck2 = plot(check_outliers(Time.aov.timeperattempt))
ck1/ck2


```

### Attempt per trial

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Anova
Time.aov.attemptpertrial <- aov(attemptpertrial ~ group, data = Time)

summary(Time.aov.attemptpertrial)
report(Time.aov.attemptpertrial)

# Checks model assumptions
ck1 = plot(check_normality(Time.aov.attemptpertrial),type = "qq")
ck2 = plot(check_outliers(Time.aov.attemptpertrial))
ck1/ck2

# Perform the Tukey HSD test
posthoc.attemptpertrial <- TukeyHSD(Time.aov.attemptpertrial)

# Print the results
print(posthoc.attemptpertrial)
```

## Tool switching

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Anova
Switch.aov <- aov(toolswitching ~ group, data = Switch)

summary(Switch.aov)
report(Switch.aov)

# Checks model assumptions
ck1 = plot(check_normality(Switch.aov),type = "qq")
ck2 = plot(check_outliers(Switch.aov))
ck1/ck2

# Perform the Tukey HSD test
posthoc.switch <- TukeyHSD(Switch.aov)

# Print the results
print(posthoc.switch)
```

## Number of tools

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Anova
Ntools.mod2aov <- aov(nbtool ~ group, data = Ntools)

summary(Ntools.mod2aov)
report(Ntools.mod2aov)

# Checks model assumptions
ck1 = plot(check_normality(Ntools.mod2aov),type = "qq")
ck2 = plot(check_outliers(Ntools.mod2aov))
ck1/ck2

# Perform the Tukey HSD test
posthoc.ntools <- TukeyHSD(Ntools.mod2aov)

# Print the results
print(posthoc.ntools)
```

## Distance

```{r, message=FALSE, fig.height=10, fig.width=10, fig.align='center', dpi = 300, warning=FALSE}
##### Anova
Distance.aov <- aov(distance ~ group, data = Distance)

summary(Distance.aov)
report(Distance.aov)

# Checks model assumptions
ck1 = plot(check_normality(Distance.aov),type = "qq")
ck2 = plot(check_outliers(Distance.aov))
ck1/ck2
```

# Plotting

```{r, fig.height=11.7, fig.width=23, fig.align='center', dpi = 300}
SR = Time%>%
  ggplot( aes(x = group, y = sr,color = group))+
  geom_point(position = position_jitterdodge(),size=7, alpha=0.35)+
  stat_summary(fun.data = mean_se, geom = "pointrange",size=3,linewidth=2.5)+
  geom_signif(y_position = c(108), xmin = c(1), xmax = c(2),
              annotation=c("*"), tip_length=0, color = 'black',
              textsize = 30,size = 2.5, vjust = 0.5)+
  scale_colour_manual(values=palette1)+
  scale_x_discrete(label = c('PRG','NRG','Control'))+
  labs(y = "Success rate (%)")+
  coord_cartesian(xlim = c(1.13, 2.9), ylim = c(10,114))+
  theme_classic(base_size = 40)+
  theme(legend.position = "none",
        axis.title.x = element_blank(), axis.line = element_blank())

TimeXAttemp = Time%>%
  ggplot( aes(x = group, y = timeperattempt,color = group))+
  geom_point(position = position_jitterdodge(),size=7, alpha=0.35)+
    stat_summary(fun.data = mean_se, geom = "pointrange",size=3,linewidth=2.5)+
  scale_colour_manual(values=palette1)+
  scale_x_discrete(label = c('PRG','NRG','Control'))+
  scale_y_continuous(labels=function(x)x/1000)+
  labs(y = "Attempt time (sec)")+
  coord_cartesian(xlim = c(1.13, 2.9))+
  theme_classic(base_size = 40)+
  theme(legend.position = "none",
        axis.title.x = element_blank(), axis.line = element_blank())

AttemptXTrial = Time%>%
  ggplot( aes(x = group, y = attemptpertrial,color = group))+
  geom_point(position = position_jitterdodge(),size=7, alpha=0.35)+
  stat_summary(fun.data = mean_se, geom = "pointrange",size=3,linewidth=2.5)+
  geom_signif(y_position = c(6.2), xmin = c(1), xmax = c(2),
              annotation=c("**"), tip_length=0, color = 'black',
              textsize = 30,size = 2.5, vjust = 0.5)+
  scale_colour_manual(values=palette1)+
  scale_x_discrete(label = c('PRG','NRG','Control'))+
  labs(y = "# of attempts")+
  coord_cartesian(xlim = c(1.13, 2.9), ylim = c(1,6.5))+
  theme_classic(base_size = 40)+
  theme(legend.position = "none",
        axis.title.x = element_blank(), axis.line = element_blank())

Switch_p = Switch%>%
  ggplot( aes(x = group, y = toolswitching,color = group))+
  geom_point(position = position_jitterdodge(),size=7, alpha=0.35)+
  stat_summary(fun.data = mean_se, geom = "pointrange",size=3,linewidth=2.5)+
  geom_signif(y_position = c(105), xmin = c(1), xmax = c(2),
              annotation=c("*"), tip_length=0, color = 'black',
              textsize = 30,size = 2.5, vjust = 0.5)+
  scale_colour_manual(values=palette1)+
  scale_x_discrete(label = c('PRG','NRG','Control'))+
  labs(y = "Tool switching (%)")+
  coord_cartesian(xlim = c(1.13, 2.9), ylim = c(0,110))+
  theme_classic(base_size = 40)+
  theme(legend.position = "none",
        axis.title.x = element_blank(), axis.line = element_blank())


NumberTool = Ntools%>%
  ggplot( aes(x = group, y = nbtool,color = group))+
  geom_point(position = position_jitterdodge(),size=7, alpha=0.35)+
  stat_summary(fun.data = mean_se, geom = "pointrange",size=3,linewidth=2.5)+
  geom_signif(y_position = c(3.1,3.5), xmin = c(1,1), xmax = c(2,3),
              annotation=c("**","*"), tip_length=0, color = 'black',
              textsize = 30,size = 2.5, vjust = 0.5)+
  scale_colour_manual(values=palette1)+
  scale_x_discrete(label = c('PRG','NRG','Control'))+
  labs(y = "# of tools")+
  coord_cartesian(xlim = c(1.13, 2.9), ylim = c(0.5,3.6))+
  theme_classic(base_size = 40)+
  theme(legend.position = "none",
        axis.title.x = element_blank(), axis.line = element_blank())

Distance_p = Distance%>%
  ggplot( aes(x = group, y = distance,color = group))+
  geom_point(position = position_jitterdodge(),size=7, alpha=0.35)+
  stat_summary(fun.data = mean_se, geom = "pointrange",size=3,linewidth=2.5)+
  scale_colour_manual(values=palette1)+
  scale_x_discrete(label = c('PRG','NRG','Control'))+
  labs(y = "Distance (pixels)")+
  coord_cartesian(xlim = c(1.13, 2.9))+
  theme_classic(base_size = 40)+
  theme(legend.position = "none",
        axis.title.x = element_blank(), axis.line = element_blank())

FIN = wrap_plots(SR, AttemptXTrial, TimeXAttemp, NumberTool, Switch_p, Distance_p, ncol = 3)+
  plot_annotation(tag_levels = 'A') +
  theme(plot.tag = element_text(size = 60, hjust = 0))



ggsave(filename = paste(output,'FinalPlotAnova.svg', sep = ''), FIN,
       width = 23*1.5, height = 11.7*1.5, units = "in", dpi = 300)

ggsave(filename = paste(output,'FinalPlotAnova.jpg', sep = ''), FIN,
       width = 23*1.5, height = 11.7*1.5, units = "in", dpi = 300)
ggsave(filename = paste(output,'FinalPlotAnova.tiff', sep = ''), FIN,
       width = 23*1.5, height = 11.7*1.5, units = "in", dpi = 300)

FIN
```
